%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage{hyperref}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Sergii Gryshkevych} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}
%\smallskip 
% Horizontal line after name; adjust line thickness by changing the '1pt'
 
%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------
 
\section{CONTACT INFORMATION}  

+46 70 731 03 32\\
\href{mailto:s.gryshkevych@gmail.com}{\nolinkurl{s.gryshkevych@gmail.com} }

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

\section{PERSONAL INFORMATION}

Citizenship: Sweden, Ukraine\\
Date of birth: 10 Oct 1988\\
GitHub: \url{www.github.com/grishasergei}\\
Stackoverflow: \url{www.stackoverflow.com/users/5215538/sergii-gryshkevych}\\
LinkedIn: \url{www.linkedin.com/in/sergii-gryshkevych-79035ba3}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}


{\sl Software Developer} \hfill Aug 2017 -- Present \\
RaySearch Laboratories, Stockholm, Sweden\\
I am a member of a team that develops an oncology information system RayCare. Key responsibilities are managing patient data and integration with other RaySearch products and hospital information systems.

{\sl Master Thesis Project in Image Analysis and Machine Learning} \hfill Jun -- Dec 2016 \\
Vironova, Stockholm, Sweden \\
Developed a prototype of an image classification system based on convolutional neural networks. My prototype was benchmarked and compared against the current Vironovas model and it demonstrated high levels of accuracy and performance. For this project I used Python and machine learning libraries TensorFlow and Keras.


{\sl Software Developer} \hfill Jan 2012 -- Jul 2017 \\
ISEC Systems, Stockholm, Sweden\\
Developed and maintained an asset management system. My key responsibilities within the team were to research and implement valuation techniques of fixed income and financial derivatives products; implement new features in close cooperation with customers. 

%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Developed four ``user friendly" forecasting systems each of which produces 18 to 139 individual reports. 
%\item Developed or improved almost all IFPS programs used for financial reports. 
%\end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
 
\section{EDUCATION}  

{\sl Computational Science, Master's degree} \hfill Sep 2014 -- Jan 2017 \\
Uppsala University, Sweden\\ \\
{\sl Financial Engineering, Master's degree} \hfill Sep 2010 -- Jun 2012 \\
M{\"a}lardalen University, V{\"a}ster{\aa}s, Sweden\\ \\
{\sl Business Mathematics, Bachelor} \hfill Sep 2005 -- Jun 2009 \\
Kyiv National University, Kyiv, Ukraine\\ 


%----------------------------------------------------------------------------------------
%	SKILLS
%---------------------------------------------------------------------------------------- 

\section{SKILLS}
{\sl Programming languages: } Python, C, C\#, Delphi \\
{\sl Software Engineering: } Git, Scrum, Agile Development, Linux \\
{\sl Scientific computing: } Keras (top 5\% on Stackoverflow), TensorFlow, Neural Networks, Image Analysis, SciPy, Pandas
\pagebreak
%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
 
\section{CERTIFICATIONS}  
\bigskip
{\sl Statistical Thinking in Python I} \hfill 2018 \\
DataCamp, \href{https://www.datacamp.com/statement-of-accomplishment/course/26d7d4322b1819ca476d42047f2560da16a0d09b}{see certificate} \\\\ 
{\sl Statistical Thinking in Python II} \hfill 2018 \\
DataCamp, \href{https://www.datacamp.com/statement-of-accomplishment/course/0361db1eb15e9ddeb5fd778d93a2e0b93e3927b1}{see certificate} \\\\ 
{\sl Manipulating DataFrames with pandas} \hfill 2018 \\
DataCamp, \href{https://www.datacamp.com/statement-of-accomplishment/course/7508f1816070bc730dd15d8440f2bbb87bf3674f}{see certificate} \\ 


%----------------------------------------------------------------------------------------
%	PERSONAL PROJECTS
%----------------------------------------------------------------------------------------

\section{PERSONAL PROJECTS} 
{\sl The Murals of Kyiv }\\
\url{www.kyivmural.com} \\
This website is a collection of street art objects found in Kyiv. Developed  in Python and Hosted on Digital Ocean. 

{\sl ConViz }\\
\url{www.github.com/grishasergei/conviz} \\
ConViz is a tutorial that explains how to visualize weights and output of convolutional layers in TensorFlow.

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

\section{LANGUAGES} 

English \hfill full professional proffciency\\
Swedish \hfill professional working proffciency\\
Ukrainian \hfill native proffciency\\
Russian \hfill native proffciency

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}